SDR enhancement by clouds \\\large{A Short Subtitle}

### 2023-11-27 article/article.qmd
Commit 2023-11-27 20:14

abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date: last-modified
bibliography:  [bibliography.bib, Mainreferences.bib]
format:
  elsevier-pdf:
    keep-tex:     true
    journal:
      name:       Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  docx: default
  html: default

@@

[@Bais2013; @Bennie2008]

>>>>

abstract: |
  This is the abstract. Lorem ipsum dolor sit amet, eu efficitur justo rutrum at. Sed at tempus elit.
keywords: 
  - keyword1
  - keyword2
date:          last-modified
bibliography:  [bibliography.bib]
format:
  elsevier-pdf:
    keep-tex:     true
    journal:
      name:       Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
  docx: default
  html: default

@@

### 2023-11-27 article/article.tex
Commit 2023-11-27 20:14

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{tcolorbox}[enhanced jigsaw, leftrule=.75mm, colframe=quarto-callout-important-color-frame, colbacktitle=quarto-callout-important-color!10!white, toptitle=1mm, bottomtitle=1mm, rightrule=.15mm, bottomrule=.15mm, opacitybacktitle=0.6, breakable, coltitle=black, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, titlerule=0mm, opacityback=0, left=2mm, arc=.35mm, toprule=.15mm, colback=white]

@@

\citep{Bais2013, Bennie2008}

@@

\renewcommand\refname{References}
  \bibliography{bibliography.bib,Mainreferences.bib}

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, interior hidden, breakable, frame hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-important-color!10!white, opacityback=0, titlerule=0mm, arc=.35mm, title=\textcolor{quarto-callout-important-color}{\faExclamation}\hspace{0.5em}{gcff}, toprule=.15mm, coltitle=black, breakable, bottomtitle=1mm, rightrule=.15mm, colframe=quarto-callout-important-color-frame, opacitybacktitle=0.6, toptitle=1mm, bottomrule=.15mm, leftrule=.75mm, left=2mm, colback=white]

@@

@@

\renewcommand\refname{References}
  \bibliography{bibliography.bib}
